\stdpopsim: a community toolkit for population genetic simulation

### 2019-12-06 popSimManu.tex
typo fixed

\subsection*{Model QC procedures}
As a consortium we have agreed to a standardized proceedure for model inclusion
into \stdpopsim that allows for rigorous quality control. Imagine Developer A
wants to introduce a new model into \stdpopsim. Developer A implements the
demographic model for the relevant organism along with a series of required
unit tests and documentation. This model is submitted as a Pull Request,
where it is evaluated by a reviewer and then included as `preliminary', 
B
but is not linked to the online documentation nor the command line interface.
Inclusion of a preliminary model triggers a QC issue, and a second developer, 
Developer B, then independently reimplements the model from the relevant
primary sources and adds an automatic unit test for equality between the
QC implementation and the preliminary production model. If the two
implementations are equal the original model is included in \stdpopsim.
If not, we move to an arbitration process whereby the A and B first try
to work out the details of what went wrong. If that fails, the original
authors of the published model A is trying to implement must be contacted
to resolve ambiguities. This process can lead to cycles of revision of 
the implementation from Developers A and B but allows the project to assure
quality. Indeed we have already had a number of interesting cases of arbitration
to this point. Further details of our QC process can be found in our
\href{https://stdpopsim.readthedocs.io/en/latest/development.html#}{developer documentation}.

>>>>

\subsection*{Model QC procedures}
As a consortium we have agreed to a standardized proceedure for model inclusion
into \stdpopsim that allows for rigorous quality control. Imagine Developer A
wants to introduce a new model into \stdpopsim. Developer A implements the
demographic model for the relevant organism along with a series of required
unit tests and documentation. This model is submitted as a Pull Request,
where it is evaluated by a reviewer and then included as `preliminary', 
but is not linked to the online documentation nor the command line interface.
Inclusion of a preliminary model triggers a QC issue, and a second developer, 
Developer B, then independently reimplements the model from the relevant
primary sources and adds an automatic unit test for equality between the
QC implementation and the preliminary production model. If the two
implementations are equal the original model is included in \stdpopsim.
If not, we move to an arbitration process whereby the A and B first try
to work out the details of what went wrong. If that fails, the original
authors of the published model A is trying to implement must be contacted
to resolve ambiguities. This process can lead to cycles of revision of 
the implementation from Developers A and B but allows the project to assure
quality. Indeed we have already had a number of interesting cases of arbitration
to this point. Further details of our QC process can be found in our
\href{https://stdpopsim.readthedocs.io/en/latest/development.html#}{developer documentation}.
